Supplementary Materials for: The promise of community-driven preprints in ecology and evolution

### 2024-10-15 docs/supp.qmd
Update to supplement by adding new Table S1

---
title: "Supplementary Materials for: The promise of community-driven preprints in ecology and evolution"
bibliography: ../bib/refs.bib
csl: ../bib/proceedings-of-the-royal-society-b.csl
format:
  html:
    toc: true
    output-file: index.html
    toc-location: left
    toc-depth: 3
    toc-title: "**Table of Contents**"
    theme: simplex
    embed-resources: true
    code-fold: show
    code-tools: true
    number-sections: true
    fontsize: "12"
    max-width: "10"
    code-overflow: wrap
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'FigureS'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "FigureS"
  tbl-prefix: "TableS"
---

@@

>>>>

---
title: "Supplementary Materials for: The promise of community-driven preprints in ecology and evolution"
bibliography: ../bib/refs.bib
csl: ../bib/proceedings-of-the-royal-society-b.csl
format:
  html:
    toc: true
    output-file: index.html
    toc-location: left
    toc-depth: 3
    toc-title: "**Table of Contents**"
    theme: simplex
    embed-resources: true
    code-fold: show
    code-tools: true
    number-sections: true
    fontsize: "12"
    max-width: "10"
    code-overflow: wrap
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure S'
  tbl-title: 'Table S'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure S"
  tbl-prefix: "Table S"
---

@@

## Publication time by article type 
@tbl-time provides a breakdown of publication time by article type.

```{r}
#| label: tbl-time
#| tbl-cap: Time between preprint submission and publication for different article types.

# Load in the table(
  tbl_time <- read.csv(here("output", "tables", "preprints_pub_only_stats.csv"))[,-1]

# Flx
  tbl <- flextable::flextable(tbl_time)  %>% 
    flextable::set_table_properties(width = .5)  %>% 
    flextable::set_header_labels("type_of_preprint" = "Article Type", "mean_time" = "Mean (days)", "sd_time" = "SD (days)", "n" = "N") %>% flextable::align(align = "center") 
    tbl
```
